|

### 2021-09-29 article/articleCustomerDropoutMembership.Rmd
upd

TODO: Estava aqui... fit the model for the five clusters... compare the performance with the model without
clusters... corrigir acima para selecionar só as features.. Explorart-SNE for better visualization...

```{python createModelClusters, eval=FALSE, echo=FALSE, cache = TRUE, warning = FALSE}
# Building training and testing sets for the clusters
for cluster in df_members.cluster.unique():
    # Number of samples in the dataset
    df_members_cluster = df_members[df_members.cluster == cluster]
    N = df_members_cluster.shape[0]
    index_train, index_test = train_test_split(range(N), test_size = 0.4)
    data_train = df_members_cluster[features].loc[index_train].reset_index( drop = True )
    data_test  = df_members_cluster[features].loc[index_test].reset_index( drop = True )

    # Creating the X, T and E inputs
    X_train, X_test = df_members_cluster[features], data_test[features]
    T_train, T_test = df_members_cluster[time_column], data_test[time_column]
    E_train, E_test = df_members_cluster[event_column], data_test[event_column]

    # Fitting the model
    csf = RandomSurvivalForestModel(num_trees=200)
    csf.fit(X_train, T_train, E_train, max_features='sqrt', max_depth=5, min_node_size=20)
    c_index = concordance_index(csf, X_test, t_test, e_test)
    ibs = integrated_brier_score(csf, X_test, t_test, e_test, t_max=12, figure_size=(12,5))
    results_clusters = compare_to_actual(csf, X_test, t_test, e_test, is_at_risk = False,  figure_size=(12, 6), 
                                metrics = ['rmse', 'mean', 'median'])
    print(results_clusters)
```

>>>>

TODO: Estava aqui... fit the model for the five clusters... compare the performance with the model without
clusters... corrigir acima para selecionar só as features.. Explorar t-SNE for better visualization...

```{python createModelClusters, eval=TRUE, echo=FALSE, cache = TRUE, warning = FALSE}
# Building training and testing sets for the clusters
for cluster in df_members.cluster.unique():
    # Number of samples in the dataset
    df_members_cluster = df_members[df_members.cluster == cluster]
    X = df_members_cluster.copy()
    t = df_members_cluster['years_membership']
    e = df_members_cluster['dropout']
    X.drop(axis=1, columns=['years_membership','dropout'])
    X_train, X_test, t_train, t_test, e_train, e_test = train_test_split(X, t, e, random_state=0)
    print(f"The cluster {cluster} as a size of {X.shape[0]}")
    # Fitting the model
    csf = RandomSurvivalForestModel(num_trees=200)
    csf.fit(X_train, t_train, e_train, max_features='sqrt',
        max_depth=5, min_node_size=20)

    c_index = concordance_index(csf, X_test, t_test, e_test)

    ibs = integrated_brier_score(csf, X_test, t_test, e_test, t_max=12, figure_size=(12,5))

    results = compare_to_actual(csf, X_test, t_test, e_test, is_at_risk = False,  
                                figure_size=(12, 6), metrics = ['rmse', 'mean', 'median'])
    print(results)
